---
title: "Basic Use"
output: rmarkdown::html_vignette
vignette: >
%\VignetteIndexEntry{Basic Use}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  ---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>",
eval = FALSE
)
```


### Introduction
The easiest way to get started building your app is with the `buildElectricApp()` function. This is a "metafunction" that calls the other functions of electricShine in the order that the package was intended to build apps. 

If you want more control (e.g. icons haven't yet been implemented)...until a more thorough vignette is written, you can use source code of `buildElectricApp()` as a guide to step through the build process.


### Getting Started


#### The metafunction

`buildElectricApp()` has the following arguments (default values are listed):

```{r}
appName = "My_Package"
productName = "productName"
semanticVersion = "0.0.0"
buildPath = NULL
MRANdate = Sys.Date() - 3
functionName = NULL
githubRepo = NULL
localPath = NULL
only64 = FALSE
packageName = NULL
```



- `appName` will be what users see (e.g. shortcut name)

- `buildPath` is the directory your app will be built into (where you will find the `exe`, etc.)

- `MRANdate` This determines your R and package versions. Must be a date in the format `YYYY-MM-DD`.
For now, you must manually any non-CRAN packages manually

- `only64`, whether your app is only 64bit (determines how much the R-installation is trimmed)

- `packageName`	can be empty if Github repo/base path is same as your shiny package name


One of the following, but not both must be provided:

- `githubRepo` 	GitHub username/repo of your the shiny-app package (e.g. 'chasemc/demoAPP')

- `localPath` path to your shiny-app package (should be installable through `install.packages()`)

Your app must have a function to start the app.  

- `functionName` this is the name of the function (e.g. `run_app`)


This function needs to be able to accomodate recieving a TCP port and so I have provided an example below.  Replace the four `packageName`'s below with the name of your shiny-app package. Replace the two `app_ui` with your package's `app_ui` function name. Replace the two `app_server` with your package's `app_server` function name. The `packageName::app_ui()` should retain the `()`; and the `packageName::app_server` has no `()`.

```{r}
run_app <- function(port = NULL) {
  
  if (is.null(port)) {
    shiny::shinyApp(ui = packageName::app_ui(),
                    server = packageName::app_server)
  } else {
    port <- try(as.integer(port))
    if (is.integer(port) && port > 0L) {
      shiny::shinyApp(ui = packageName::app_ui(),
                      server = packageName::app_server,
                      options = list(port = port))
    }
  }
  
}
```



#### The build

By running the `electricShine::buildElectricApp()` function your R session will start doing the following things:

- Install nodejs into your electricShine package folder.
- Download R from the MRAN date you provided
- Download the js dependencies (electron, etc) from npm (npm is like CRAN)
- Begin the build of your app

This will take some time depending on your internet speed, and computer. The build step is the longest and can take minutes (seems to be IO-limited so a fast hard drive will work best).

### The results

In the directory your specified in `buildPath`, you will find a new folder named what you chose for `appName`. Directly inside you will find the raw electron build. Your new electron `.exe` can be found in `buildPath/appName/dist`, where `appName` is what you assigned `buildElectricApp(appName = )`. 


Advanced: If you want to test the electron app without installing. You can open cmd.exe and `cd` to `buildPath/appName` and if you have nodejs installed and in your `PATH`, use the command `npm start` to initiate the app. 

Advanced: If you want to make changes before creating the exe- run the `electricShine::buildElectricApp()` with `build = FALSE` and make your changes within `buildPath/appName`. When you're ready to build the installer run the following, using the same `buildPath` and `appName` as in `electricShine::buildElectricApp()`.

```{r}
appPath <- file.path(buildPath, appName)

electricShine::runBuild(nodePath = NULL,
                        npmPath = NULL,
                        appPath = appPath,
                        node = file.path(system.file(package = "electricShine"), "nodejs"))
```








