---
title: "Create an app from a package on Github"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{App from Github Repo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(electricShine)
```

If your Shiny app package is hosted on github you can install using `git_host = "github"`.

The `git_repo`  argumnt is used the same as the `repo` argumentfor `remotes::install_github()`

In the example below, we install the `demoApp` repository from my accoun `chasemc` at git commit `8426481`.

All other arguments for `remotes::install_github()` can be provided as a list using the argument `package_install_opts`. In the example below we set the equivalent of `remotes::install_github(type=binary)` so that we only install binary packages from CRAN even if there is a newer source version. We also set the equivalent of  `remotes::install_github(dependencies = c("Depends", "Imports"))`. 

```{r}
buildPath <- tempdir()

electricShine::electrify(app_name = "My_App",
                         short_description = "My demo application",
                         semantic_version = "1.0.0",
                         build_path = buildPath,
                         function_name = "run_app",
                         git_host = "github",
                         git_repo = "chasemc/demoApp@8426481",
                         package_install_opts = list(type = "binary",
                                                     dependencies = c("Depends", 
                                                                      "Imports")
                                                     ),
                         cran_like_url = "https://cran.r-project.org"
                         )
```